---
title: "UCLA Assessment"
author: "Shicheng_Chen"
date: "April 13, 2019"
output: html_document
---
#Loading Package
```{r}
library(readr)
library(dplyr)
library(highcharter)
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(reshape2)
```

#Loading Data
```{r}
data_a <- read_csv("imm10_a.csv")
data_b <- read_csv("imm10_b.csv")
data_l <- read_csv("imm10_lev2.csv")
```

#Data Cleaning
##Checking duplications.
```{r}
which(duplicated(data_a))
which(duplicated(data_b))
which(duplicated(data_l))

```

##Combiming data as Public and Private schools
```{r}
data_sch = rbind(data_a,data_b)
data_pub = subset(data_sch, data_sch$SCHID %in% subset(data_l,data_l$MPUBLIC == 1)$SCHID)
data_prv = subset(data_sch, data_sch$SCHID %in% subset(data_l,data_l$MPUBLIC != 1)$SCHID)
```

##Checking missing values
```{r}
summary(data_pub)
summary(data_prv)
summary(data_l)
```

#EDA Over all 
##Sex Ratio Male:Female
```{r}
tmp = data_sch
tmp$SCHID = as.factor(tmp$SCHID)
tmp %>% group_by(SCHID) %>% summarize(SexRatio = round(sum(SEX == 2)/sum(SEX == 1),4)) %>% arrange(-SexRatio) %>% hchart('scatter',hcaes(x = 'SCHID',y = 'SexRatio', size = 'SexRatio',color = 'SCHID')) %>% hc_add_theme(hc_theme_538()) %>% hc_title(text = 'Male : Female Ratio for All Schools' ) %>%  hc_yAxis(title = list(text = "Ratio"),
        plotLines = list(list(
          value = 1,
          color = '#ff0000',
          width = 3,
          zIndex = 4,
          label = list(text = "Male : Female -> 1:1 Line",
                       style = list( color = '#ff0000', fontWeight = 'bold'   )
          )))) %>%
  hc_xAxis(title = list(text = "School ID"),
           opposite = TRUE,
           minorTickInterval = "auto",
           minorGridLineDashStyle = "LongDashDotDot",
           showFirstLabel = FALSE,
           showLastLabel = FALSE,
           plotBands = list(
             list(from = 4.5, to = 5.5, color = "rgba(100, 0, 0, 0.1)",
                  label = list(text = "Private School")))) 
#This is a chart for all school male comapre to female ratio, the larger circle means this school have higher ratio. From the plot we noticed before school id 68493, all of those schools are having more females than males. Our private school, has more males, the ratio is 1:0.8611. 
```

##SES Level
```{r}
tmp = data_l
tmp$SCHID = as.factor(tmp$SCHID)
tmp %>% group_by(SCHID) %>% summarize(SESlvl = MMEANSES) %>% arrange(-SESlvl)%>% hchart('scatter',hcaes(x = 'SCHID',y = 'SESlvl', size = 'SESlvl',color = 'SCHID')) %>% hc_add_theme(hc_theme_538()) %>% hc_title(text = 'SES for All Schools' ) %>%  hc_yAxis(title = list(text = "SES Level"),
        plotLines = list(list(
          value = 0,
          color = '#ff0000',
          width = 3,
          zIndex = 4,
          label = list(text = "Positive SES Line",
                       style = list( color = '#ff0000', fontWeight = 'bold'   )
          )))) %>%
  hc_xAxis(title = list(text = "School ID"),
           opposite = TRUE,
           minorTickInterval = "auto",
           minorGridLineDashStyle = "LongDashDotDot",
           showFirstLabel = FALSE,
           showLastLabel = FALSE,
           plotBands = list(
             list(from = -0.5, to = 0.5, color = "rgba(100, 0, 0, 0.1)",
                  label = list(text = "Private School")))) 
tmp = data_sch
tmp$SCHID = as.factor(tmp$SCHID)
tmp %>% group_by(SCHID) %>% summarise(LowSES = sum(SES < 0,na.rm=T),n=n()) %>% mutate(PerctengeLowSES = round(LowSES/n,2)) %>% arrange(-PerctengeLowSES) %>% hchart('scatter', hcaes(x = 'SCHID', y = 'PerctengeLowSES', size = 'PerctengeLowSES', corlor = 'SCHID')) %>%  hc_add_theme(hc_theme_538()) %>% hc_title(text = 'Low SES Percentage for All Schools' ) %>% hc_xAxis(title = list(text = "School ID"),
           opposite = TRUE,
           minorTickInterval = "auto",
           minorGridLineDashStyle = "LongDashDotDot",
           showFirstLabel = FALSE,
           showLastLabel = FALSE,
           plotBands = list(
             list(from = 8.5, to = 9.5, color = "rgba(100, 0, 0, 0.1)",
                  label = list(text = "Private School")))) 
#Above the red line, will receive a positive SES.
```


##Teacher Ratio:
```{r}
tmp = data_l
tmp$SCHID = as.factor(tmp$SCHID)
tmp$MPUBLIC = ifelse(tmp$MPUBLIC == 1,'PUB','PRV')
tmp %>% group_by(SCHID) %>% summarize(TeacherRetio = MRATIO) %>% arrange(-TeacherRetio) %>% hchart('scatter',hcaes(x = 'SCHID',y = 'TeacherRetio', size = 'TeacherRetio',color = 'SCHID')) %>% hc_add_theme(hc_theme_538()) %>% hc_title(text = 'Teacher Ratio' ) %>%  hc_yAxis(title = list(text = "TeacherRetio"),
        plotLines = list(list(
          value = mean(tmp$MRATIO),
          color = '#ff0000',
          width = 3,
          zIndex = 4,
          label = list(text = "Mean of Teacher Ratio",
                       style = list( color = '#ff0000', fontWeight = 'bold'   )
          )))) %>%
  hc_xAxis(title = list(text = "School ID"),
           opposite = TRUE,
           minorTickInterval = "auto",
           minorGridLineDashStyle = "LongDashDotDot",
           showFirstLabel = FALSE,
           showLastLabel = FALSE,
           plotBands = list(
             list(from = 8.5, to = 9.5, color = "rgba(100, 0, 0, 0.1)",
                  label = list(text = "Private School")))) 
```

#EDA Between Public and Private
##Sex Percentage
```{r}
tmp = data_sch
tmp$PUB = ifelse(tmp$SCHID %in% subset(data_l,data_l$MPUBLIC == 1)$SCHID,'PUB','PRV')
tmp$SEX = ifelse(tmp$SEX == 1, 'Male','Female')
tmp %>% group_by(PUB,SEX) %>% summarise(n = n()) %>% mutate(percentage = round(n/sum(n)*100)) %>% hchart('bar',hcaes(x = 'PUB', y = 'percentage',group = 'SEX')) %>% hc_plotOptions(series = list(stacking = 'normal')) %>% hc_title(text = 'Percentage of Sex Between Public School and Private School' ) %>% hc_add_theme(hc_theme_flat())
```

##Female Score and Study Time
```{r}
tmp = data_sch
tmp$PUB = ifelse(tmp$SCHID %in% subset(data_l,data_l$MPUBLIC == 1)$SCHID,'PUB','PRV')
tmp$SEX = ifelse(tmp$SEX == 1, 'Male','Female')
hcboxplot(x = tmp$MATH,var = tmp$PUB) %>% hc_chart(type = 'column') %>%hc_add_theme(hc_theme_ffx())
highchart() %>%
  hc_add_series_boxplot(x = tmp$HOMEWORK,by = tmp$PUB , name = 'Homework',outliers = F) %>%
  hc_add_series_boxplot(x = tmp$PARENTED,by = tmp$PUB , name = 'Parent',outliers = F) %>% hc_add_theme(hc_theme_ffx())

```

##Race Combination in Public and Priavet Schools
```{r}
tmp = data_sch
tmp$PUB = ifelse(tmp$SCHID %in% subset(data_l,data_l$MPUBLIC == 1)$SCHID,'PUB','PRV')
tmp$SEX = ifelse(tmp$SEX == 1, 'Male','Female')
tmp$RACE = ifelse(tmp$RACE == 1,'Asian',ifelse(tmp$RACE == 2,'Hispanic',ifelse(tmp$RACE ==3,'Black',ifelse(tmp$RACE==4,'White','Native American'))))
Pie_Pub= tmp %>% subset(tmp$PUB == "PUB") %>%
  group_by(RACE) %>%
  summarise(volume = n()) %>%
  mutate(share=volume/sum(volume)) %>%
  ungroup() %>% 
  arrange(desc(volume)) %>%
  mutate(RACE=factor(RACE, levels = as.character(RACE)))%>%
  ggplot(aes(x="", y= share, fill=RACE)) +
  geom_col() +
  geom_text(aes(label = scales::percent(round(share,3))), position = position_stack(vjust = 0.5))+
  coord_polar(theta = "y") + 
  theme_void()

Pie_Tst = tmp %>% subset(tmp$PUB == "PRV") %>%
  group_by(RACE) %>%
  summarise(volume = n()) %>%
  mutate(share=volume/sum(volume)) %>%
  ungroup() %>% 
  arrange(desc(volume)) %>%
  mutate(RACE=factor(RACE, levels = as.character(RACE)))%>%
  ggplot(aes(x="", y= share, fill=RACE)) +
  geom_col() +
  geom_text(aes(label = scales::percent(round(share,3))), position = position_stack(vjust = 0.5))+
  coord_polar(theta = "y") + 
  theme_void()
ggarrange(Pie_Ctl,Pie_Tst,labels = c("Public School", "Private School"))
```

#Analysis
##Correlation Heatmap on MathScore Female
```{r}
tmp = subset(data_sch,data_sch$SEX == 2)
tmp = tmp[which(tmp$SES != 'NA'),]
tmp$PUB = ifelse(tmp$SCHID %in% subset(data_l,data_l$MPUBLIC == 1)$SCHID,0,1)
tmp = tmp[,-c(1,2,8)]
summary(tmp)
newtmp = round(cor(tmp),2)
newtmp = melt(newtmp)
ggplot(newtmp, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Variable\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed() +geom_text(aes(Var2, Var1, label = value), color = "black", size = 4)
```

##ANOVA
```{r}
tmp = subset(data_sch,data_sch$SEX == 2)
tmp = tmp[which(tmp$SES != 'NA'),]
tmp$PUB = ifelse(tmp$SCHID %in% subset(data_l,data_l$MPUBLIC == 1)$SCHID,0,1)
tmp = tmp[,-c(1,2,8)]
fit.lm = lm(data = tmp,MATH~WHITE+SES+HOMEWORK+PARENTED+PUB)
summary(fit.lm)
par(mfrow = c(2,2))
plot(fit.lm)
fit.aov = aov(fit.lm)
summary(fit.aov)
confint(fit.aov)
```






































